---
  output: word_document
---

  
```{r, echo = FALSE, message = FALSE, warning = FALSE}
load(file="Markdown test.RData")
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(pander)
library(plyr)
```

# General

What | Result | Explanation of the tables |
:---------------------- | :------------- | :-----------------------
  Number of students| `r n.stud` |   For each question the frequency, percentage and item rest correlations (IRC)
Number of questions | `r n.item` |  from every answer option are diplayed. The IRC should be (highly) positive
Average score | `r round(mean(rowSums(input.correct)), digits = 3)`  | for the right answer option and low for the wrong answer option(s).
Standard deviation | `r round(sd(rowSums(input.correct)), digits = 3)`  | |
  Cronbach's alpha | `r cronbach`  | |
Standard error | `r round(sd(rowSums(input.correct) * sqrt(1 - cronbach)), digits = 3)` | |


```{r, echo=FALSE, eval=TRUE, results = "asis"}
# Creating results for each item
item.list <- list() # Creates list to put item output in
colnames1 <- c("Answer Option", "Frequency", "Percentage", "IRC")
colnames2 <- c("Answer Option", "Frequency", "Percentage", "IRC", "Correct")


# Filling a list with frequency, percentage and IRC for total and each answer options.
# Every item gets a seperate data frame in the list.
# If no answeroptions are present, only the correct statistics are displayed.
# If there are more than 14 answer options, only the correct statistics are displayed to conserve space.
# The list is used for the first part of the output and is modified to a data frame to make the plots with the answer options.

for (i in 1:n.item) {
  if (n.answer.op[i] > 0 & n.answer.op[i] < 15) {
    Correct <- c(ifelse(key[, i] == 1, "Correct", "Incorrect"), "Incorrect")
    
    # Frequency is also stored at this point, but not used.
    # in case someone wants to alter the script to display the frequency instead of the percentage
    item.list[[i]] <- data.frame(c(LETTERS[1:n.answer.op[i]], "Missing"),
                                 c(freq.answer.op[c(2:(n.answer.op[i] + 1), 1), i]),
                                 c(perc.answer.op[c(2:(n.answer.op[i] + 1), 1), i]),
                                 c(answer.op.tot.cor[c(2:(n.answer.op[i] + 1), 1), i]),
                                 Correct,
                                 row.names = NULL)
    colnames(item.list[[i]]) <- colnames2
  } else {
    item.list[[i]] <- data.frame("Total", item.sum[i],
                                 item.perc[i],
                                 item.tot.cor[i])
    colnames(item.list[[i]]) <- colnames1
  }
}

#Create item names
if(!exists("item.names")) item.names = 1:n.item
items <- paste("Item", item.names, sep = " ")
names(item.list) <- items
```

# Item statistics

```{r pander, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
# Create tables per item with frequency chosen, percentage chosen and the item-rest correlation. Correct answers are highlighted in bold
panderOptions('knitr.auto.asis', FALSE)
for(i in 1:length(item.list))
{
  emphasize.strong.rows(which(key[,i] == 1, arr.ind = TRUE))
  pander(item.list[i])
}
```

# Correct percentage

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9}
# Create a dataframe with only the correct statistics. This is used in the general item plots
correct.df <- data.frame(factor(1:n.item), item.sum,
                         item.perc, item.tot.cor)
names(correct.df)[1] <- "item"

### Frequency Plot for total items
bar_freq <- ggplot(correct.df, aes(item, item.perc, fill = item.perc)) # Create chart with Answer Option on x-axis and percentae correct on y-asix
bar_freq <-  bar_freq + geom_bar(stat = "identity") + # Create Bar chart
  scale_fill_gradient2(low = "red", mid = "green", high = "red", midpoint = 50, limits = c(0, 100), name = "")  + # Create colour boundray: Green = "right" according to psychometrics, a value of 50% correct is ideal.
  coord_cartesian(ylim = c(0, 100)) + # Change y-axis limit to constant
  labs(x = "Item", y = "Percentage") + #x axis name
  theme(strip.text.x = element_text(size = 7) , axis.text.x = element_text(size = 8), # Change font size of item names and Answer options
        axis.ticks.x = element_line(size = .4)) +
  theme_bw()

bar_freq

```

# Item rest correlations

```{r, echo = FALSE, eval = TRUE, warning= FALSE, fig.width = 9}

### IRC Bar Plot for total items
bar_IRC <- ggplot(correct.df, aes(item, item.tot.cor, fill = item.tot.cor)) # Create chart with Answer_Option on x-axis and IRC on y-asix
bar_IRC <-  bar_IRC + geom_bar(stat = "identity") + # Create Bar chart
  scale_fill_gradient(low = "red", high = "green", limits = c(-.1, .4), name = "")  + # Create colour boundray: Green = "right" (low for wrong answer options, high for right answer options)
  #    coord_cartesian(ylim = c(ifelse(min(correct.df$item.tot.cor < 0), min(correct.df$item.tot.cor), 0), 1)) + # Change y-axis limit to constant
  labs(x = "Item", y = "Item Rest Correlation") + # Change titles and x axis name
  theme(strip.text.x = element_text(size = 7), axis.text.x = element_text(size = 8), # Change font size of item names and Answer options
        axis.ticks.x = element_line(size = .4)) +
  theme_bw()

bar_IRC
```


# Percentage chosen per item

Percentage chart(s) per question and per answer options. The green bars represent the right answer options. The color of the border represents the desirability (50% for the right answer options, low for the wrong answer options)

```{r, echo = FALSE, eval = TRUE, warning= FALSE, fig.width = 9}
# Create data frame of all the items which have answer options. This is used to make barplots per answer option
# Create extra variables to make the bar plots
for(i in 1:n.item) {
  #Create right order on the x-axis (Missingness last)
  if (any(key[, i] != 0)) {
    item.list[[i]]$Ans_Factor <- factor(item.list[[i]]$"Answer Option")
    item.list[[i]]$Col_scale <- as.numeric(item.list[[i]]$Correct) * 2 - 3
    item.list[[i]]$IRC_col_scale <- with(item.list[[i]], IRC * Col_scale)
    item.list[[i]]$Perc_col_scale <- with(item.list[[i]], Percentage)
  }
}

if (any(key != 0)) {
  Ans.Opt.df <- ldply(item.list[n.answer.op != 0], data.frame)
  names(Ans.Opt.df)[1] <- "id"
  Ans.Opt.df$Answer.Option <- gsub("Missing", "Mis", Ans.Opt.df$Answer.Option)
  Ans.Opt.df$Ans_Factor <- gsub("Missing", "Mis", Ans.Opt.df$Ans_Factor)
  Ans.Opt.df$Ans_Factor <- factor(Ans.Opt.df$Ans_Factor,
                                  levels = c(LETTERS[1 : max(n.answer.op)], "Mis"))
  Ans.Opt.df$id <- factor(Ans.Opt.df$id , levels = items[n.answer.op != 0])
  Ans.Opt.df$Perc_col_scale[Ans.Opt.df$Correct == "Correct"] <- 100 - Ans.Opt.df$Perc_col_scale[Ans.Opt.df$Correct == "Correct"]
}

# Calculating which questions are displayed on which plot. The number of plots is determined by a max of 80 bars per plot and then dividing all answer options over the plot
if (any(key != 0)) {
  Max.Answ.Opts = 80
  Tot.Answ.Opts = nrow(Ans.Opt.df)
  n.plots = ceiling(Tot.Answ.Opts / Max.Answ.Opts)
  Answ.Opts.Per.Plot = Tot.Answ.Opts / n.plots
  
  items.in.plot <- list(unique(Ans.Opt.df[1 : Answ.Opts.Per.Plot, 1]))
  if(n.plots > 1){
    for(i in 2:n.plots)
      items.in.plot[[i]] <- unique(Ans.Opt.df[((i - 1) * Answ.Opts.Per.Plot) : (i * Answ.Opts.Per.Plot), 1])
    items.in.plot[[i]] <- items.in.plot[[i]][-1]
  }
}
```
   
   
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.width = 9}    
  # Create the plots of the frequencies per answer option
if (any(key != 0)) {
  for(i in 1:n.plots){ 
    bar_freq1 <- ggplot(Ans.Opt.df[Ans.Opt.df$id %in% items.in.plot[[i]], ],  # Select subset of questions
                        aes("Answer Option", Percentage, fill = Correct, colour = Perc_col_scale)) # Create chart with Answer Option on x-axis and frequency on y-asix
    bar_freq1 <- bar_freq1 + geom_bar(aes(x = Ans_Factor), stat = "identity") + # Create Bar chart
      facet_grid(. ~ id, scales = "free_x", space = "free_x") + # Display the different items
      scale_fill_manual(values = c("Incorrect" = "Red" ,"Correct" = "Green"), guide=FALSE) + # Fill in the bars: Green right answer options, Red wrong answer options
      scale_colour_gradient(low = "green", high = "red", guide = FALSE) + # Create colour boundray: Green = "right" (low for wrong answer options, high for right answer options)
      coord_cartesian(ylim = c(0, 100)) + # Change y-axis limit to constant
      labs(x = "Answer Options") + # x axis name
      theme(strip.text.x = element_text(size = 7), # Font size of labels of the facets: e.g. Item 1
            axis.text.x = element_text(size = 5.5), # Font size of text by tick marks of the x-asis
            axis.ticks.x = element_line(size = .1), # Size of the tick marks on the x-asis
            axis.title.x = element_text(size = 11), # Font size of the x-asis title
            axis.title.y = element_text(size = 11), # Font size of the y-axis title 
            title = element_text(size = 9)) + # Font size of the overall title
      theme_bw()
    
    print(bar_freq1)
  }
}
```

# Item rest correlations per item

IRC chart(s) per question and per answer options. The green bars represent the right answer options. The color of the border represents the desirability (high for the right answer options, low for the wrong answer options)

```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.width = 9}
 
if (any(key != 0)) {
  # Creating IRC plots 
  
  for(i in 1:n.plots){ 
    bar_IRC1 <- ggplot(Ans.Opt.df[Ans.Opt.df$id %in% items.in.plot[[i]], ]  # Select subset of first plots
                       , aes("Answer Option", IRC, fill = Correct, colour = IRC_col_scale)) # Create chart with Answer Option on x-axis and IRC on y-asix
    bar_IRC1 <-  bar_IRC1 + geom_bar(aes(x = Ans_Factor), stat = "identity") + # Create Bar chart
      facet_grid(. ~ id, scales = "free_x", space = "free_x") + # Display the different items
      scale_fill_manual(values = c("Incorrect" = "Red", "Correct" = "Green"), guide = FALSE) + # Fill in the bars: Green right answer options, Red wrong answer options
      scale_colour_gradient(low = "green", high = "red", guide = FALSE) + # Create colour boundray: Green = "right" (low for wrong answer options, high for right answer options)
      coord_cartesian(ylim = c(ifelse(min(Ans.Opt.df$IRC) < -.3, min(Ans.Opt.df$IRC) - .01, -.3),
                               ifelse(max(Ans.Opt.df$IRC) > .4, max(Ans.Opt.df$IRC) + .01, .4))) + # Change y-axis limit to either the maximum IRC or .4 and minimum IRC or -.3
      labs(x = "Answer Options") + #x axis name
      theme(strip.text.x = element_text(size = 7), # Font size of labels of the facets: e.g. Item 1
            axis.text.x = element_text(size = 5.5), # Font size of text by tick marks of the x-asis
            axis.ticks.x = element_line(size = .1), # Size of the tick marks on the x-asis
            axis.title.x = element_text(size = 11), # Font size of the x-asis title
            axis.title.y = element_text(size = 11), # Font size of the y-axis title 
            title = element_text(size = 9)) + # Font size of the overall title
      theme_bw()
    
    print(bar_IRC1)
  }
}
```

# Empirical Cumulative Distribution Function

Empirical Cumulative Distribution Function showing all possible scores and the percentage of students that scored that number or higher

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9}
# Create cumulative histogram

totaal <- rowSums(input.correct)
heights <- length(totaal)
h = heights[1]

n <- sort(unique(totaal))

for(i in 1:length(n))
{
  h = h - length(totaal[totaal == n[i]])
  heights = c(heights, h)
}

cesuurlijnen <- seq(0.2, 0.8, 0.2) * nrow(input.correct)
gridlijnen <- round(seq(0, nrow(input.correct), (nrow(input.correct)/25)), 0)

gridlijnen <- gridlijnen[-grep(paste(cesuurlijnen, collapse = "|"), gridlijnen)]

heights <- heights[1:length(unique(totaal))]
percent <- heights/length(totaal)*100
df <- data.frame(score = sort(unique(totaal)), total = heights, percent = round(percent,2))

h <- ggplot(data = df, aes(x = score, y = total)) + 
    geom_hline(yintercept = c(gridlijnen), linetype = "solid", colour = "gray80") +  
  geom_hline(yintercept = cesuurlijnen, linetype = "dashed", size = 0.75, colour = "black") +
  geom_histogram(stat = "identity", binwidth = 1) + 
  xlab("Total score") + ylab("% students with score or higher") + 
  scale_y_continuous(breaks = c(0, cesuurlijnen, nrow(input.correct)), labels = c(seq(0, 100, 20))) +
  scale_x_continuous(limits = c(0, ncol(input.correct)), breaks = 1:ncol(input.correct)) + 
  theme_bw() +
  theme(panel.grid = element_blank())

print(h)
```
  
